Digital History in Finland, 1488-1828

### 2016-06-23 inst/examples/manuscript-krakow.Rmd
Rmd update

Why Fennica has huge drop in 1700s. Do some publisher disappear (TODO). Let us look at top publication places in Fennica:

```{r drop1700, echo=FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=6, out.width="280px"}
selected.places = names(top(subset(df0, catalog == "Fennica"), "publication_place", 10))
for (myplace in selected.places) {
  # Use timeinterval year intervals
  catal = "Fennica"
  minyear = 1650
  maxyear = 1750

>>>>

Why Fennica has huge drop in 1700s. Do some publisher disappear (TODO). Let us look at top publication places during the period 1650-1750 in Fennica:

```{r drop1700, echo=FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=6, out.width="280px"}

  catal = "Fennica"
  minyear = 1650
  maxyear = 1750
  df = subset(df0, catalog == catal)
  df <- subset(df, publication_year >= minyear & publication_year < maxyear)
  mydf = df

selected.places = names(top(mydf, "publication_place", 6))

for (myplace in selected.places) {

  df = subset(mydf, publication_place == myplace)

  # Use timeinterval year intervals
  timeinterval <- 1
  df$timeunit <- round(df$publication_year/timeinterval)*timeinterval
